Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
most of photometric calibration text added

\section{Custom Photometric Calibration}
\label{sec:calib}

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products. 
}

@@

% cite software packages such as numpy, scipy, matplotlib ??

>>>>

\section{Custom Photometric Calibration}
\label{sec:calib}
In order to combine frames across multiple mission phases, it is necessary
to place all exposures on a common photometric calibration such that
the multiplicative scalings of all images are consistent. Each L1b
image includes a \verb|MAGZP| header keyword which gives the official
Vega zero-point of that exposure. These zero-points are essentially
predictions of system throughput based on predictors such as beam splitter
assembly temperature, and have been shown to differ by up to several percent 
from time-dependent gain variations measured empirically with single-exposure
photometry of standard sources \citep{cutri13, cutri15}.

We therefore sought to achieve an empirical photometric calibration
across all mission phases accurate at the several mmag level. Our basic
strategy was to analyze repeat measurements of compact sources near the 
ecliptic poles, where WISE gathers data every $\sim$$95$ minutes throughout the 
entire mission. Specifically, our sample consists of moderately bright,
unsaturated compact sources with $|\beta| > 85^{\circ}$, and avoiding a wedge 
defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ to exclude the LMC. The 
positions and nominal average magnitudes of our moderately bright source
sample were drawn from the AllWISE Source Catalog, selecting sources with 
10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ \verb|w2mpro| $<$ 11.7 and with
\verb|w?cc_map|=0 in the band of interest.

These spatial, magnitude and flag cuts yield samples of $\sim$109,000 
($\sim$27,000) unique calibrator sources in W1 (W2). We perform aperture 
photometry using \verb|djs_phot| with a 27.5$''$ radius for each calibrator 
source in every L1b exposure in which it appears sufficiently far from the 
image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
single-epoch aperture fluxes which form the basis for our derived 
time-dependent zero points. The typical calibrator source contributes 
$\gtrsim$400 epochs of photometry.

We sought a photometic calibration with time resolution of one day. 
% mention that single-epoch fluxes grouped into one-day bins
% mention that single-epoch fluxes of each source were normalized
% to the average (median?) flux measured during the All-sky phase, and 
% that the AllWISE phase zero points were taken at face value, and
% that we used the single-exp ecl pole photometry to verify that the zero point 
% was stable at the $<=1 mmag$ level of the All-sky phase of the mission

Figure 1 shows our derived zero points for each WISE mission phase as 
compared to the \verb|MAGZP| values obtained from the L1b headers. When
using our custom zero points to scale L1b images, we employ an 
interpolation scheme based on a series of tapered polynomials and 
error functions, meant to smooth out noise in our per-day zero point
determinations. In general, our per-day zero points agree reasonably
well with the \verb|MAGZP| values, although there are often 
percent-level differences, and at times disagreement at the several percent
level. In some cases the time-trends within a particular mission phase
show qualitative disagreement (e.g. both W1 and W2 during the NEOWISE
mission phase).

% do i want to mention comparison between ecliptic north and south poles ??

% caption of zero point figure needs to clarify the '4band', '3band', '2band' ..
% terminology

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products.

This research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}

This research makes use of data products from the Wide-field Infrared
Survey Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration. This publication
also makes use of data products from NEOWISE, which is a project of the Jet
Propulsion Laboratory/California Institute of Technology, funded by the
Planetary Science Division of the National Aeronautics and Space
Administration. }

@@

% cite software packages such as numpy, scipy, matplotlib ??
% mention idlutils
